### 2015-05-18 writing/SNLI paper/corpus.tex
Paper update.

need for new corpus

@@

@@

@@

\subsection{Statistics}

what's new
- size
- grounding

data will be freely available

SICK presented an important challenge, we try to deliver on it.

aim to surpass sick in both size and r consistency

Since our goal is to evaluate the quality of the single sentence representations in our model, we train an entailment classifier that has access only to the output of our sentence representation model, and not to any of the word or phrase representations that it used. We encourage future users of this corpus to evaluate their models in this way when possible. Our classifier is simply a stack of three 100d (NONLIN) layers, with the bottom layer taking the concatenated sentence representations as input and the top layer feeding a softmax classifier, all trained jointly with the representation model itself.

We use captions from the Flickr30k corpus \cite{hodoshimage} as the left hand side of each relation pair. That corpus ...

We randomly selected individual captions from that corpus to use in our own corpus, though in the interest of encouraging more complex source sentences without discarding too much source data, we downsample sentences with lengths of under 90 characters so that these sentences make up only half of our corpus, rather than the original 69\%.

... licencing ...

The instructions for this phase were integrated into the design of the data collection interface. The text of those instructions is shown in Figure~\ref{instructions-1}. We chose to use three classes, corresponding to ENTAILMENT, CONTRADICTION, and NEUTRAL classes used in SICK.

We will show you the caption for a photo. We will not show you the photo. Using only the caption and what you know about the world:
\begin{itemize}
\item Write one alternate caption that is \textbf{definitely} a \textbf{true} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors."}
\item Write one alternate caption that \textbf{might be} a \textbf{true} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors."}
\item Write one alternate caption that is \textbf{definitely} a \textbf{false} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors." This is different from the maybe correct category because its impossible for the dogs to be both running and sitting.}
\end{itemize}
\textbf{Problems} (optional)   If something is wrong with the caption that makes it difficult to understand, do your best above and let us know here.
% \bottomrule
\caption{\label{instructions-1}Examples of training data from the newly collected entailment corpus.}
\end{figure}

We posted 15.5k ImageFlickr captions. We showed each of the first 10k captions to five workers, yielding fifteen reponse sentences per source caption, with five assigned to each of the three labels. Then, to ensure maximal diversity in the test set, we showed the remaining 5.5k source captions to one worker each,  yielding only three responses per source caption.

We collected 143,023 pairs, after excluding less than 100 worker responses in which the worker reported that they could not understand the source caption, or in which a field was accidentally left blank. The average worker response sentence was 7.8 words long. 1100 workers participated in the task.

pre-verification distribution:

Recompute after removing blanks:
29305 contra
29304 neut
29305 ent

% ditto examples
%
\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{6.5cm}cp{6.5cm}}
  \toprule
A busy street with building lined up and people walking down the street outside and nighttime. &\ii{entailment}	&People lined up\\
\rule{0pt}{3ex}Two men stand in an electric outdoor lift. &\ii{neutral}	& The two men are inspectors for the FDA, waiting to inspect the second level of the pharmaceutical plant.\\
\rule{0pt}{3ex}A young redheaded girl, wearing a yellow shirt, black pants, and sneakers, jumping in a grassy field with blue skies and wispy clouds in the background. &\ii{entailment}	& A girl jumps in a grassy field\\
\rule{0pt}{3ex}A crowd of people, one with a guitar, are standing in the street under the 7th Avenue street sign. &\ii{neutral}	& The crowd listening to the man play guitar.\\
\rule{0pt}{3ex}A woman wearing bike shorts and a skirt is riding a bike and carrying a shoulder bag.  &\ii{contradiction}& A woman driving a car.\\
    \bottomrule
  \end{tabular}
  \caption{\label{examplesofscedata}The instructions presented to workers during data collection.}
\end{table*}

@@

\paragraph{Validation}

The majority of the sentence pairs in the corpus have not been reviewed by anyone since their construction as part of the data collection Mechanical Turk task, except to remove blank responses and responses some pairs which the original author flagged for review. However, in order to measure the quality of our corpus, and in order to construct maximally useful testing and development sets, we did perform an additional round of validation for about 54k examples.

This validation phase is not fundamentally different from the Mechanical Turk labeling task used for the SICK entailment data: we present workers with pairs of sentences (in our case, in batches of five at a time), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original composer of the pair.

\begin{figure}
\footnotesize
%\toprule
TODO: VALIDATION INSTRUCTIONS
%\bottomrule\\

\caption{\label{instructions-2}The instructions presented to workers during data validation.}
\end{figure}

@@

No sentence overlap btw train and test and dev.

Mention antonyms for motivation against unsup tasks

% LHS length distribution: {1: 1, 2: 42, 3: 156, 4: 1095, 5: 3882, 6: 12120, 7: 26514, 8: 37434, 9: 44028, 10: 49245, 11: 50919, 12: 48363, 13: 43314, 14: 38121, 15: 33183, 16: 27621, 17: 23250, 18: 20247, 19: 18513, 20: 16386, 21: 13746, 22: 12066, 23: 9183, 24: 7131, 25: 6198, 26: 5007, 27: 3963, 28: 3438, 29: 2631, 30: 1959, 31: 1956, 32: 1434, 33: 1086, 34: 912, 35: 897, 36: 774, 37: 453, 38: 618, 39: 291, 40: 330, 41: 249, 42: 180, 43: 225, 44: 162, 45: 108, 46: 87, 47: 60, 48: 36, 49: 90, 50: 21, 51: 66, 52: 51, 53: 36, 54: 24, 55: 63, 56: 18, 57: 15, 58: 6, 59: 27, 60: 6, 61: 3, 62: 3, 63: 3, 64: 6, 65: 3, 66: 3, 67: 6, 68: 6, 69: 18, 70: 15, 71: 3, 72: 15, 73: 3, 75: 15, 79: 3, 82: 15}

% RHS length distribution: {1: 39, 2: 1011, 3: 7980, 4: 29471, 5: 61196, 6: 74094, 7: 93600, 8: 85851, 9: 61359, 10: 46711, 11: 33241, 12: 22844, 13: 15994, 14: 11047, 15: 7601, 16: 5312, 17: 3732, 18: 2631, 19: 1878, 20: 1325, 21: 911, 22: 642, 23: 449, 24: 357, 25: 217, 26: 168, 27: 138, 28: 84, 29: 67, 30: 46, 31: 26, 32: 31, 33: 23, 34: 16, 35: 19, 36: 8, 37: 12, 38: 4, 39: 5, 40: 2, 41: 4, 42: 2, 43: 1, 44: 1, 48: 1, 51: 1, 55: 2, 56: 1, 60: 1, 62: 1}

@@

>>>>

% TODO: Rewrite and expand motivation here (CP?)

@@

% TODO: Rewrite and expand (CP?)

@@

We used Amazon Mechanical Turk for data collection. In each individual task, a worker was presented with premise scene descriptions from a preexisting corpus, and asked to supply hypotheses that fit each of our three labels (\ii{entailment}, \ii{neutral}, and \ii{contradiction}).

For the premises, we used the Flickr30k corpus \cite{hodoshimage}, a collection of approximately 160k captions from that corpus (corresponding to about 30k images) collected in an earlier crowdsourced effort. The captions were not authored by the photographers who took the source images, they tend to contain relatively literal scene descriptions that are suited to our approach, rather than those typically associated with personal photographs (as in their example: ``Our trip to the Olympic Peninsula''). We presented each caption to at least one worker, and some to more than one. With the exception of a handful that were flagged by workers as excessively difficult, at least three labeled pairs are available for each caption.

The instructions that we provided to the workers are shown in Fig.~\ref{instructions-1}. Below the instructions were three fields for each of three requested sentences, corresponding to our \ii{entailment}, \ii{neutral}, and \ii{contradiction} labels, a fourth field (marked optional) for reporting problems, and a link to an FAQ page. That FAQ grew over the course of data collection, but discussed disallowed techniques (e.g., reusing the same sentence for many different prompts, which we saw in a few cases), sentence length and complexity (we did not enforce a minimum length, and we allowed bare NPs as well as full sentences), and logistical issues around payment timing.

We will show you the caption for a photo. We will not show you the photo. Using only the caption and what you know about the world:
\begin{itemize}
\item Write one alternate caption that is \textbf{definitely} a \textbf{true} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors."}
\item Write one alternate caption that \textbf{might be} a \textbf{true} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors."}
\item Write one alternate caption that is \textbf{definitely} a \textbf{false} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors." This is different from the maybe correct category because its impossible for the dogs to be both running and sitting.}
\end{itemize}
\caption{\label{instructions-1}The instructions used on Mechanical Turk for data collection.}
\end{figure}

% TODO: Do we need statistics about the number/distribution of workers?
% TODO: Do we need statistics about how much of ImageFlickr we rejected/double-annotated?

@@

The majority of the sentence pairs in the corpus have not been reviewed by anyone since their construction as part of the data collection Mechanical Turk task, except to remove blank responses and responses some pairs which the original author flagged for review. However, in order to measure the quality of our corpus, and in order to construct maximally useful testing and development sets, we did perform an additional round of validation for about 54k (TODO) examples.

This validation phase is not fundamentally different from the Mechanical Turk labeling task used for the SICK entailment data: we present workers with pairs of sentences (in our case, in batches of five at a time), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original composer of the pair. The instructions were broadly similar to the instructions for initial data collection shown in Fig.~\ref{instructions-1}, and linked to a similar FAQ.

\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{7.5cm}lp{5.5cm}}
  \toprule
A young man in a striped hoodie looks at an artistic Levi's advertisement that says "We are all workers." & \ii{entailment} & There is a man in a hoodie looking at an advertisement.\\
\rule{0pt}{3ex}Two men on laptops in a dark room. & \ii{entailment} & Two men are on their laptops.\\
\rule{0pt}{3ex}A naked baby and toddler smear each other in paint. & \ii{neutral} & The kids are in the bathtub.\\
\rule{0pt}{3ex}A woman is focusing on her game of curling. & \ii{neutral} & There is a women playing a game indoors\\
\rule{0pt}{3ex}A group of people dressed in green and white are dancing in a circle outside of a white building. & \ii{contradiction} & A group performs indoors.\\
\rule{0pt}{3ex}A balding professor giving a lecture to students on the topic of "opportunity". & \ii{neutral} & A female professor with hair giving a lecture to students.\\
% TODO: Replace with *validated* examples from the post-rc2 training set, include all 5 labels
    \bottomrule
% From 1.0rc2
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from SNLI.}
\end{table*}

\subsection{The distributed corpus}

@@

@@

@@

\paragraph{Parses}

The distributed corpus includes parses for every sentence produced by the Stanford PCFG Parser \cite{klein2003accurate}, both in the standard PTB format and in the binarized unlabeled format used by tree-structured neural network models, as in \S\ref{sentence-embedding}.

% TODO (CM?)
